{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-11-30 ident_manu.Rnw
local sensitivity analysis results section done

\documentclass[letterpaper,12pt,oneside]{article}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{lineno}
\usepackage{array}
\usepackage{times}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage[position=t]{subfig}
\usepackage{paralist}
\usepackage[noae]{Sweave}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{fixltx2e}
% \usepackage{showlabels}
\bibpunct{(}{)}{,}{a}{}{,}

@@

%acronyms
\acrodef{chla}[chl-\textit{a}]{chlorophyll \textit{a}}
\acrodef{cgem}[CGEM]{Coastal General Ecosystem Model}
\acrodef{do}[O$_2$]{dissolved oxygen}
\acrodef{gom}[GOM]{Gulf of Mexico}
\acrodef{lcs}[LCS]{Louisiana continental shelf}
\acrodef{marb}[MARB]{Mississippi-Atchafalaya River Basin}
\acrodef{zerod}[0-D]{zero-dimensional}

@@

<<echo = FALSE>>=
p1z1pars <- par_tst()

# number of parameters in each category
nparms <- parcats2(as_df = TRUE) %>% 
  filter(shrt %in% p1z1pars) %>% 
  .$cats %>% 
  table %>% 
  as.list

@@

Parameter sensitivity was evaluated by comparing the results from the default model setup to an alternative, more complex setup with alternative switches (\cref{tab:strcs}).  The scenarios used different equations to represent structural relationships of phytoplankton growth patterns with temperature, nutrient uptake, cell quotas, \ac{chla} to carbon ratios, photosynthesis dynamics, and specific growth limits. The default scenario modelled phytoplankton growth with temperature as a sigmoidal function \citep{Eldridge10}, nutrient uptake as Michaelis-Menten kinetics \citep{Dugdale67}, internal cell quotas following \citet{Droop73}, \ac{chla} to carbon ratios as a simple regression \citep{Murrell14}, light-dependence of photosynthesis with photoinhibition \citep{Platt80}, and a specific growth rate following Leibig's law of the minimum.  Conversely, the complex scenario used switches that modelled relationships between phytoplankton growth with temperature using the Arrhenius model \citep{Geider97}, nutrient uptake as proposed by \citet{Lehman75} and modified in \citet{Geider98}, internal cell quotas following \citet{Flynn03}, \ac{chla} to carbon ratios following \citet{Cloern95}, light-dependence of photosynthesis that is nutrient dependent \citep{Flynn03}, and a specific growth rate that is nutrient dependent.  Complete details are provided as supplementary material to \citetalias{LehrterIR}.

@@

The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.  In addition to \ac{do}, other state variables that were evaluated were \ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.  Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIR}).

@@

% for inline
<<echo = FALSE, eval = F, cache = F>>=
data(sens_ests_all)
data(sens_ests_cat)

# number of parameters in each category
bycat <- table(sens_ests_cat$Category)
nms <- names(bycat)
bycat <- as.numeric(bycat)
names(bycat) <- nms
bycat <- toeng(bycat)

# percent of parameters in each category
lncats <- table(sens_ests_cat$Category) %>%
  `/` (table(sort(parcats2(as_df = TRUE)$cats))) %>%
  `*` (100) %>%
  form_fun(nsm_val = 0) %>%
  as.list %>%
  lapply(., paste0, '\\%')

# L1 range
sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>%
  sens_ests_cat[., ] %>%
  mutate(
   error = sapply(error, scinot),
   Parameter = par_txt(Parameter)
   )

# L1 range within categories
sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>%
  lapply(., function(x){

  with(x, which(error %in% range(error))) %>%
    x[., ] %>%
    mutate(
      Parameter = par_txt(Parameter),
      error = sapply(error, scinot)
    )

  }
)

# average L1, all and by category
sensave <- scinot(mean(sens_ests_cat$error))
sensave_cat <- split(sens_ests_cat, sens_ests_cat$Category) %>%
  lapply(., function(x) scinot(mean(x$error)))

# phyto errors
phytogrps <- filter(sens_ests_cat, Category == 'Phytoplankton') %>%
  separate(Parameter, c('parm', 'grp'), sep = '_') %>%
  group_by(grp) %>%
  summarise(grpave = mean(error)) %>%
  arrange(-grpave) %>%
  mutate(grpave = sapply(grpave, scinot))

# zoop errors
zoopgrps <- filter(sens_ests_cat, Category == 'Zooplankton') %>%
  separate(Parameter, c('parm', 'grp'), sep = '_') %>%
  group_by(grp) %>%
  summarise(grpave = mean(error)) %>%
  arrange(-grpave) %>%
  mutate(grpave = sapply(grpave, scinot))
@

%' \subsection{Local sensitivity analysis}
%' Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 178 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/178, 0)}\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables). Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{sensave}.  Within categories, sensitivity ranged from \Sexpr{sensrngcat$Optics$error[1]} (\Sexpr{sensrngcat$Optics$Parameter[1]}) to \Sexpr{sensrngcat$Optics$error[2]} (\Sexpr{sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{sensrngcat$`Organic Matter`$error[1]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{sensrngcat$`Organic Matter`$error[2]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{sensrngcat$Phytoplankton$error[1]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{sensrngcat$Phytoplankton$error[2]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) for phytopankton, \Sexpr{sensrngcat$Temperature$error[1]} (\Sexpr{sensrngcat$Temperature$Parameter[1]}) to \Sexpr{sensrngcat$Temperature$error[2]} (\Sexpr{sensrngcat$Temperature$Parameter[2]}) for temperature, and \Sexpr{sensrngcat$Zooplankton$error[1]} (\Sexpr{sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{sensrngcat$Zooplankton$error[2]} (\Sexpr{sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{fig:sensplo}, bottom).  Average sensitivity values in each category were $L1 = $ \Sexpr{sensave_cat$Optics} for optics, \Sexpr{sensave_cat$`Organic Matter`} for organic matter, \Sexpr{sensave_cat$Phytoplankton} for phytoplankton, \Sexpr{sensave_cat$Temperature} for temperature, and \Sexpr{sensave_cat$Zooplankton} for zooplankton.  Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied. Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ \Sexpr{phytogrps[1, 2]}, \Sexpr{phytogrps[2, 2]}), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$). Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ \Sexpr{zoopgrps[1, 2]}, \Sexpr{zoopgrps[2, 2]} for groups one and two).
%' Response of \ac{do} to parameter perturbations was not uniform across the time series.  \Cref{fig:sensplo} shows variation for the top parameters within each category.  Because FishTank does not include a spatial component, the estimated \ac{do} trend describes a closed, heterotrophic system where respiration processes eventually remove all \ac{do} from the model space.  The initial decrease in the time series reflects change from the initial conditions outside of the growing seasons (i.e., January, February), the spring/summer increase represents production associated with expected seasonal growth, and the remaining time series from August to the end of year shows complete removal of \ac{do} as respiration processes dominate metabolic activity. Although this time series is not a realistic depiction of an actual system, the biogeochemical model behaves as expected in the absence of the hydrodynamic model.  Accordingly, the interpretation of sensitivity results from the simple model has relevance in an ecological context.  As expected, parameter perturbations had the largest effect during the summer months, although the effects varied.  An inrease in 50\% from the parameter default values generally caused a reduction in \ac{do} during the summer, with the exception of the zooplankton parameter, \Sexpr{sensrngcat$Zooplankton$Parameter[2]}, which caused an increase in \ac{do}.  The phytoplankton parameter, \Sexpr{sensrngcat$Phytoplankton$Parameter[2]}, had the largest effect such that the \ac{do} time series was similar to the default output in April/May, whereas a dramatic decrease was observed in the remaining months.  The effects of perturbations early in the time series (January, February) showed similar patterns such that a reduction in \ac{do} was most common, particularly for the optics (\Sexpr{sensrngcat$Optics$Parameter[2]}) and phytoplankton (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) parameters.
%' \subsection{Subset identifiability}

@@

%' Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).  For the first selection heuristic, all sensitive parameters from the optics ($n = $ \Sexpr{scinot(h1_id$Optics[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$Optics[[2]]}) and organic matter ($n = $ \Sexpr{scinot(h1_id$`Organic Matter`[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$`Organic Matter`[[2]]}) categories were selected, whereas \Sexpr{toeng(h1_id$Phytoplankton[[1]])[[1]]} were selected for phytoplankton ($\gamma = $ \Sexpr{h1_id$Phytoplankton[[2]]}), \Sexpr{toeng(h1_id$Temperature[[1]])[[1]]} for temperature ($\gamma = $ \Sexpr{h1_id$Temperature[[2]]}), and \Sexpr{toeng(h1_id$Zooplankton[[1]])[[1]]} for zooplankton ($\gamma = $ \Sexpr{h1_id$Zooplankton[[2]]}).  For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]}, with a majority from the phytoplankton category, \cref{tab:identall1}).  For the third heuristic, \Sexpr{toeng(h3_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h3_id[[2]]}) with equal representation between categories. For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.  Selection independent of category showed that including \Sexpr{par_txt(h2_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h2_brk[3], digits = 1)} to \Sexpr{scinot(h2_brk[2], digits = 1)} and equal selection within cateogies showed that including \Sexpr{par_txt(h3_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h3_brk[3], digits = 1)} to \Sexpr{scinot(h3_brk[2], digits = 1)}.  Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).  Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.  Interestingly, no parameters from the temperature category were selected.

@@

grid.arrange(
  arrangeGrob(p1, p2, ncol = 2),
  left = 'Identifiability', 
  bottom = 'Parameters in set',
  pleg, ncol = 2, widths = c(1, 0.1)
)
@

@@

grid.arrange(
  arrangeGrob(p1, p2, ncol = 2, bottom = 'Parameters in set'),
  left = 'Identifiability',
  pleg, ncol = 2, widths = c(1, 0.2)
)
@

@@

% om1 sensitivity all categories
<<om1sens, eval = T, cache = F>>=
senstab(out_var = 'OM1', tablab = 'om1sens', captxt = 'particulate organic matter', digits = 2, pow = 2, tabsize = 'footnotesize')
@

% om2 sensitivity all categories
<<om2sens, eval = T, cache = F>>=
senstab(out_var = 'OM2', tablab = 'om2sens', captxt = 'dissolved organic matter', digits = 2, pow = 2, tabsize = 'footnotesize')
@

>>>>

\documentclass[letterpaper,12pt,oneside]{article}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{lineno}
\usepackage{array}
\usepackage{times}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage[position=t]{subfig}
\usepackage{paralist}
\usepackage[noae]{Sweave}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{fixltx2e}
\usepackage[inline]{showlabels}
\bibpunct{(}{)}{,}{a}{}{,}

@@

%acronyms
\acrodef{chla}[chl-\textit{a}]{chlorophyll \textit{a}}
\acrodef{cgem}[CGEM]{Coastal General Ecosystem Model}
\acrodef{do}[O$_2$]{dissolved oxygen}
\acrodef{dom}[DOM]{dissolved organic matter}
\acrodef{gom}[GOM]{Gulf of Mexico}
\acrodef{lcs}[LCS]{Louisiana continental shelf}
\acrodef{marb}[MARB]{Mississippi-Atchafalaya River Basin}
\acrodef{pom}[POM]{particulate organic matter}
\acrodef{zerod}[0-D]{zero-dimensional}

@@

% number of parameters evaluated, total and by category
<<echo = FALSE>>=
p1z1pars <- par_tst()

# number of parameters in each category
nparms <- parcats2(as_df = TRUE) %>% 
  filter(shrt %in% p1z1pars) %>% 
  .$cats %>% 
  table %>% 
  as.list  
@

@@

Parameter sensitivity was evaluated by comparing the results from the default model setup to a more complex setup with alternative switches (\cref{tab:strcs}).  The scenarios used switches for different equations to represent structural relationships of phytoplankton growth patterns with temperature, nutrient uptake, cell quotas, \ac{chla} to carbon ratios, photosynthesis dynamics, and specific growth limits. The default scenario modelled phytoplankton growth with temperature as a sigmoidal function \citep{Eldridge10}, nutrient uptake as Michaelis-Menten kinetics \citep{Dugdale67}, internal cell quotas following \citet{Droop73}, \ac{chla} to carbon ratios as a simple regression \citep{Murrell14}, light-dependence of photosynthesis with photoinhibition \citep{Platt80}, and a specific growth rate following Leibig's law of the minimum.  Conversely, the complex scenario used switches that modelled relationships between phytoplankton growth with temperature using the Arrhenius model \citep{Geider97}, nutrient uptake as proposed by \citet{Lehman75} and modified in \citet{Geider98}, internal cell quotas following \citet{Flynn03}, \ac{chla} to carbon ratios following \citet{Cloern95}, light-dependence of photosynthesis that is nutrient dependent \citep{Flynn03}, and a specific growth rate that is nutrient dependent.  Complete details are provided as supplementary material to \citetalias{LehrterIR}.

@@

The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.  In addition to \ac{do}, other state variables that were evaluated were ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus.  Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIR}).

@@

% for inline
<<echo = FALSE, eval = T, cache = F>>=
data(sens_ests_cat_all)

# each state variable has:
#   txt: chr string for inline text of variable name
#   tot: total number of sensitive parameters
#   bycat: list of number of sensitive parameters in each category
#   lncat: list of percentage of sensitive parameters in each category
#   sensrng: tibble with min/max sensitivity across categories
#   sensrngcat: list of tibbles with min/max sensitivity within categories
#   sensave: numeric of overall sensitivity
#   sensavecat; list of average sensitivity by categories
loc <- loc_summ(sens_ests_cat_all)
locO2 <- loc$O2
locO2$sensavecat <- lapply(locO2$sensavecat, scinot)
locO2$sensave <- scinot(locO2$sensave)

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{locO2$tot} of the \Sexpr{length(p1z1pars)} (\Sexpr{round(100 * locO2$tot/length(p1z1pars), 0)}\% of total) evaluated parameters in FishTank (default panel \cref{fig:sensalltile}, \cref{tab:dosens}). Within each parameter category, \ac{do} was sensitive to \Sexpr{locO2$bycat$Optics} parameters for optics (\Sexpr{locO2$lncat$Optics} of all optic parameters), \Sexpr{locO2$bycat$`Organic Matter`} for organic matter (\Sexpr{locO2$lncat$`Organic Matter`}), \Sexpr{locO2$bycat$Phytoplankton} for phytoplankton (\Sexpr{locO2$lncat$Phytoplankton}), \Sexpr{locO2$bycat$Temperature} for temperature (\Sexpr{locO2$lncat$Temperature}), and \Sexpr{locO2$bycat$Zooplankton} for zooplankton (\Sexpr{locO2$lncat$Zooplankton}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{locO2$sensrng$error[1]} for \Sexpr{locO2$sensrng$Parameter[1]} (\Sexpr{tolower(locO2$sensrng$Category[1])}) to \Sexpr{locO2$sensrng$error[2]} for \Sexpr{locO2$sensrng$Parameter[2]} (\Sexpr{tolower(locO2$sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{locO2$sensave}. Within categories (excluding temperature), sensitivity ranged from \Sexpr{locO2$sensrngcat$Optics$error[1]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Optics$error[2]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{locO2$sensrngcat$`Organic Matter`$error[1]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{locO2$sensrngcat$`Organic Matter`$error[2]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{locO2$sensrngcat$Phytoplankton$error[1]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Phytoplankton$error[2]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[2]}) for phytoplankton, and \Sexpr{locO2$sensrngcat$Zooplankton$error[1]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Zooplankton$error[2]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[2]}) for zooplankton.  Average sensitivity values in each category were $L1 = $ \Sexpr{locO2$sensavecat$Optics} for optics, \Sexpr{locO2$sensavecat$`Organic Matter`} for organic matter, \Sexpr{locO2$sensavecat$Temperature} for temperature, \Sexpr{locO2$sensavecat$Phytoplankton} for phytoplankton, and \Sexpr{locO2$sensavecat$Zooplankton} for zooplankton.

<<echo = F>>=
locChla_mg_tot <- loc$Chla_mg_tot
locirradiance <- loc$irradiance
locNH4 <- loc$NH4
locNO3 <- loc$NO3
locOM1 <- loc$OM1
locOM2 <- loc$OM2
locPO4 <- loc$PO4

# average sensitivities for all
aveall <- lapply(loc, function(x){
  out <- x$sensave
  names(out) <- x$txt
  out
  }) %>% 
  unlist %>% 
  sort
names(aveall) <- gsub('^.*\\.', '', names(aveall))

# parameter category with highest average sensitivity for each st var
maxcat <- lapply(loc, function(x){

  out <- x$sensavecat %>% 
    unlist %>% 
    .[which.max(.)]

  nms <- tolower(names(out))
  out <- scinot(out)
  names(out) <- nms
  out

})

# average parameter sensitivity for categories, independent of state variables
avecat <- do.call('rbind', sens_ests_cat_all) %>% 
  split(.$Category) %>% 
  lapply(function(x) mean(x$error)) %>% 
  unlist %>% 
  sort %>% 
  sapply(scinot)
names(avecat) <- tolower(names(avecat))

Local sensitivity analyses for the additional state variables (ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus) had similar results as \ac{do} with some exceptions (\cref{fig:sensalltile,tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens}).  All additional variables were sensitive to the same parameters (\Sexpr{locO2$tot} of \Sexpr{length(p1z1pars)} evaluated), although average sensitivity differed between variables.  Average $L1$ ranged from \Sexpr{scinot(aveall[2])} for \Sexpr{names(aveall)[2]} (\cref{tab:irrsens}) to \Sexpr{scinot(aveall[length(aveall)])} for \Sexpr{names(aveall)[length(aveall)]} (\cref{tab:om2sens}).  All average sensitivity values for the state variables were higher than the average for \ac{do} ($L1$ = \Sexpr{scinot(aveall[1])}).  For each variable, $L1$ ranged from \Sexpr{locNH4$sensrng[1, 2]} (\Sexpr{locNH4$sensrng[1, 1]}) to \Sexpr{locNH4$sensrng[2, 2]} (\Sexpr{locNH4$sensrng[2, 1]}) for ammonium (\cref{tab:nh4sens}), \Sexpr{locChla_mg_tot$sensrng[1, 2]} (\Sexpr{locChla_mg_tot$sensrng[1, 1]}) to \Sexpr{locChla_mg_tot$sensrng[2, 2]} (\Sexpr{locChla_mg_tot$sensrng[2, 1]}) for \ac{chla} (\cref{tab:chlsens}), \Sexpr{locirradiance$sensrng[1, 2]} (\Sexpr{locirradiance$sensrng[1, 1]}) to \Sexpr{locirradiance$sensrng[2, 2]} (\Sexpr{locirradiance$sensrng[2, 1]}) for irradiance (\cref{tab:irrsens}), \Sexpr{locNO3$sensrng[1, 2]} (\Sexpr{locNO3$sensrng[1, 1]}) to \Sexpr{locNO3$sensrng[2, 2]} (\Sexpr{locNO3$sensrng[2, 1]}) for nitrate (\cref{tab:no3sens}), \Sexpr{locOM1$sensrng[1, 2]} (\Sexpr{locOM1$sensrng[1, 1]}) to \Sexpr{locOM1$sensrng[2, 2]} (\Sexpr{locOM1$sensrng[2, 1]}) for \ac{pom} (\cref{tab:om1sens}),  \Sexpr{locOM2$sensrng[1, 2]} (\Sexpr{locOM2$sensrng[1, 1]}) to \Sexpr{locOM2$sensrng[2, 2]} (\Sexpr{locOM2$sensrng[2, 1]}) for \ac{dom} (\cref{tab:om2sens}), and \Sexpr{locPO4$sensrng[1, 2]} (\Sexpr{locPO4$sensrng[1, 1]}) to \Sexpr{locPO4$sensrng[2, 2]} (\Sexpr{locPO4$sensrng[2, 1]}) for phosphate (\cref{tab:po4sens}).  For the parameter categories, ammonium was most sensitive to \Sexpr{names(maxcat$NH4)} parameters (average $L1$ = \Sexpr{maxcat$NH4} across all parameters in the category), \ac{chla} to \Sexpr{names(maxcat$Chla_mg_tot)} ($L1$ = \Sexpr{maxcat$Chla_mg_tat}), irradiance to \Sexpr{names(maxcat$irradiance)} ($L1$ = \Sexpr{maxcat$irradiance}), nitrate to \Sexpr{names(maxcat$NO3)} ($L1$ = \Sexpr{maxcat$NO3}), \ac{pom} to \Sexpr{names(maxcat$OM1)} ($L1$ = \Sexpr{maxcat$OM1}), \ac{dom} to \Sexpr{names(maxcat$OM2)} ($L1$ = \Sexpr{maxcat$OM2}), and phosphate to \Sexpr{names(maxcat$PO4)} ($L1$ = \Sexpr{maxcat$PO4}).  Finally, average sensititivy between parameter categories independent of the state variables ranged from \Sexpr{avecat[1]} for \Sexpr{names(avecat)[1]} (average $L1$ across all variables) to \Sexpr{avecat[length(avecat)]} for \Sexpr{names(avecat)[length(avecat)]}.

\subsection{Subset identifiability}

@@

%' Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).  For the first selection heuristic, all sensitive parameters from the optics ($n = $ \Sexpr{scinot(h1_id$Optics[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$Optics[[2]]}) and organic matter ($n = $ \Sexpr{scinot(h1_id$`Organic Matter`[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$`Organic Matter`[[2]]}) categories were selected, whereas \Sexpr{toeng(h1_id$Phytoplankton[[1]])[[1]]} were selected for phytoplankton ($\gamma = $ \Sexpr{h1_id$Phytoplankton[[2]]}), \Sexpr{toeng(h1_id$Temperature[[1]])[[1]]} for temperature ($\gamma = $ \Sexpr{h1_id$Temperature[[2]]}), and \Sexpr{toeng(h1_id$Zooplankton[[1]])[[1]]} for zooplankton ($\gamma = $ \Sexpr{h1_id$Zooplankton[[2]]}).  For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]}, with a majority from the phytoplankton category, \cref{tab:identall1}).  For the third heuristic, \Sexpr{toeng(h3_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h3_id[[2]]}) with equal representation between categories. For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.  Selection independent of category showed that including \Sexpr{par_txt(h2_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h2_brk[3], digits = 1)} to \Sexpr{scinot(h2_brk[2], digits = 1)} and equal selection within cateogies showed that including \Sexpr{par_txt(h3_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h3_brk[3], digits = 1)} to \Sexpr{scinot(h3_brk[2], digits = 1)}.  Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, \ac{pom}, \ac{dom}, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).  Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.  Interestingly, no parameters from the temperature category were selected.

@@

grid.arrange(
  arrangeGrob(p1, p2, ncol = 2),
  left = 'Identifiability', 
  bottom = 'Parameters in set',
  pleg, ncol = 2, widths = c(1, 0.1)
)

@@

grid.arrange(
  arrangeGrob(p1, p2, ncol = 2, bottom = 'Parameters in set'),
  left = 'Identifiability',
  pleg, ncol = 2, widths = c(1, 0.2)
)

@@

% om1 sensitivity all categories
<<om1sens, eval = T, cache = F>>=
senstab(out_var = 'OM1', tablab = 'om1sens', captxt = '\\ac{pom}', digits = 2, pow = 2, tabsize = 'footnotesize')
@

% om2 sensitivity all categories
<<om2sens, eval = T, cache = F>>=
senstab(out_var = 'OM2', tablab = 'om2sens', captxt = '\\acl{dom}', digits = 2, pow = 2, tabsize = 'footnotesize')
@
